---
title: "Decision Trees"
author: "Faris Alsubaie"
date: "11/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Helper packages
library(dplyr)       # for data wrangling
library(ggplot2)     # for awesome plotting

# Modeling packages
library(rpart)       # direct engine for decision tree application
library(caret)       # meta engine for decision tree application

# Model interpretability packages
library(rpart.plot)  # for plotting decision trees
library(vip)         # for feature importance
library(pdp)         # for feature effects
```


Using the Boston housing data set from the pdp package, where the response feature is the median value of homes within a census tract (cmedv):


How many internal splitting nodes optimize model performance?
What are the predicted values and SEE in the terminal nodes?
Identify the first feature split node and explain how it is splitting this feature.
Which 10 features are considered most influential? Are these the same features that have been influential in previous models?
Now perform 1-5 to the Attrition dataset, which is classification model rather than a regression model.
```{r}

```

```{r }
Boston  <- pdp::boston
split <- initial_split(Boston, strata = "cmedv", prop = 0.7)
train <- training(split)
test  <- testing(split)
```

Apply a decision tree model with all features.

```{r}
Boston <- rpart(
  formula = cmedv ~ .,
  data    = train,
  method  = "anova"
)
```

```{r}
Boston
```

```{r}
rpart.plot(Boston)
```

```{r}
plotcp(Boston)
```

```{r}
Boston <- rpart(
  formula = cmedv ~ .,
  data    = train,
  method  = "anova",
    control = list(cp = 0, xval = 10)
)

plotcp(Boston)
abline(v = 11, lty = "dashed")
```

```{r}
Boston$cptable
```

```{r}
Boston <- train(
  cmedv ~ .,
  data = train,
  method = "rpart",
  trControl = trainControl(method = "cv", number = 10),
  tuneLength = 20
)
```

```{r}
ggplot(Boston)
```

```{r}
vip(Boston, num_features = 45, geom = "point")
```
```{r}
p1 <- partial(Boston, pred.var = "rm") %>% 
  ggplot(aes(rm, yhat)) +
  geom_line()

p2 <- partial(Boston, pred.var = "lstat") %>% 
  ggplot(aes(lstat, yhat)) +
  geom_line()

p3 <- partial(Boston, pred.var = c("rm", "lstat")) %>% 
  plotPartial(levelplot = FALSE, zlab = "yhat", drape = TRUE, 
              colorkey = TRUE, screen = list(z = -20, x = -60))

# Display plots side by side
gridExtra::grid.arrange(p1, p2, p3, ncol = 3)
```

