---

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Exercises
Identify four real-life applications of supervised and unsupervised problems.
Explain what makes these problems supervised versus unsupervised.
For each problem identify the target variable (if applicable) and potential features.
Identify and contrast a regression problem with a classification problem.
What is the target variable in each problem and why would being able to accurately predict this target be beneficial to society?
What are potential features and where could you collect this information?
What is determining if the problem is a regression or a classification problem?
Identify three open source datasets suitable for machine learning (e.g., https://bit.ly/35wKu5c).
Explain the type of machine learning models that could be constructed from the data (e.g., supervised versus unsupervised and regression versus classification).
What are the dimensions of the data?
Is there a code book that explains who collected the data, why it was originally collected, and what each variable represents?
If the dataset is suitable for supervised learning, which variable(s) could be considered as a useful target? Which variable(s) could be considered as features?
Identify examples of misuse of machine learning in society. What was the ethical concern?

```{r }
#https://datahub.io/core/natural-gas#resource-natural-gas_zip
gas_prices <- read.csv("data/monthly_csv.csv")
gas_pricesD <- read.csv("data/daily_csv.csv")

```
```{r}
summary(gas_prices)
summary(gas_pricesD)
```


```{r}
dim(gas_pricesD)
mean(gas_prices$Price)
ggplot(gas_pricesD, aes(x=Price))+
geom_histogram()
```